\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage[activate={true,nocompatibility},
            final,
            tracking=true,
            kerning=true,
            spacing=true,
            factor=1100,
            stretch=10,
            shrink=10]{microtype}
\usepackage{listings}
\usepackage{xcolor}

\microtypecontext{spacing=nonfrench}

\doublespacing

\setlength\parskip{1ex}
\setlength\parindent{1em}

\begin{document}

\begin{enumerate}

\item Use the following code to illustrate the Banker’s algorithm and explain what is occurring at each step. Annotate your output to illustrate what is happening.

\textbf{First, it calls isSafe(), which runs through every other function in the class to check if something is safe. First it gathers user input, then it calculates how much each process needs to have. It then initializes a boolean array with the same number of booleans as there are processes. It iterates through the resources needed to check if there's enough resources to fulfill each processes' needs. If it succeeds, it prints a success message. Otherwise, it prints a failure message.}

\textbf{There is a line-by-line explanation of the code below.}

\end{enumerate}

\begin{center}
\lstinputlisting[language=Java,
                 basicstyle=\footnotesize \ttfamily,
                 commentstyle=\color{green},
                 keywordstyle=\color{blue},
                 stringstyle=\color{purple},
                 showstringspaces=false,
                 numbers=left,
                 numbersep=5pt,
                 numberstyle=\tiny,
                 title=\lstname]{Bankers.java}

\newpage

\begin{lstlisting}[basicstyle=\footnotesize \ttfamily,
       numbers=left,
       numbersep=5pt,
       numberstyle=\tiny,
       title=Output]
////SUCCESSFUL

Enter no. of processes and resources : 2 1 //2 processes, 1 resource
Enter allocation matrix -->
2 2 //already has 2 allocated
Enter max matrix -->
4 4 //can go up to 4
Enter available matrix -->
6 6 //there's 6 available for both processes
Allocated process : 0
Allocated process : 1
Safely allocated //(4 - 2) < 6, you're good to go


////UNSUCCESSFUL

Enter no. of processes and resources : 2 1 //2 processes, 1 resource
Enter allocation matrix -->
2 2 //already has 2 allocated
Enter max matrix -->
4 4 //can go up to 4
Enter available matrix -->
1 1 //only has 1 available for both
All proceess cant be allocated safely //(4 - 2) > 2, fails

\end{lstlisting}

\end{center}

\newpage

\begin{enumerate}
\setcounter{enumi}{1}

\item Give examples of inputs where a safe allocation of processes occurs and one where processes cannot be allocated safely.

\textbf{See Output, above. If \texttt{(allocation - max) \textgreater available}, allocation fails.}

\item What conditions cause the former to happen? The latter? Clearly indicate these in your writeup. (e.g., for all i, j, when max[i][j] \textless avail[i][j])

\textbf{See answer 2. Output contains both a failure and success and explains why; resources available were less than resources needed by a process.}

\item From a big picture perspective, why is this implementation of resource allocation so widely appreciated?

\textbf{It's so simple that it can be understood and implemented intuitively, but it solves a majority of the problems associated with resource allocation. It guarantees that resources are not exhausted, and that deadlock never occurs; it can be used to help schedulers work properly, and it prevents the deadliest errors in resource allocation, all in a function which only takes 70 ish lines of Java to implement. Its elegance and guarantees are what makes it so famous.}

\end{enumerate}

\end{document}
